### 2018-03-03 submission/manuscript.Rmd
add importance, rm conclusion, change to sig OR only model

**Results.** We quantified the odds ratios for individual bacterial genera that were associated with an individual having tumors relative to a normal colon. Among the stool samples, there were no genera that had a significant odds ratio associated with adenoma and there were `r length(crc_OR_stool$measure)` genera with significant odds ratios associated with carcinoma. Similarly, among the tissue samples, there were no genera that had a significant odds ratio associated with adenoma and there were `r length(crc_unmatched_OR_tissue$measure)` genera with significant odds ratios associated with carcinoma. Among the significant odds ratios, the association between individual taxa and tumor diagnosis was equal or below `r ifelse(max(crc_OR_stool$rr) > max(crc_unmatched_OR_tissue$rr), round(max(crc_OR_stool$rr), digits = 2), round(max(crc_unmatched_OR_tissue$rr), digits = 2))`. Because individual taxa had limited association with tumor diagnosis, we trained Random Forest classification models using the genera with the five highest and lowest odds ratios, using the entire collection of genera found in each study, and using operational taxonomic units defined based on a 97% similarity threshold. All training approaches yielded similar classification success as measured using the  Area Under the Curve. The ability to correctly classify individuals with adenomas was poor and the ability to classify individuals with carcinomas was considerably better using sequences from stool or tissue.

**Conclusions.** This meta-analysis confirms previous results indicating that individuals with adenomas cannot be readily classified based on their bacterial community, but that those with carcinomas can. Regardless of the dataset, we found a subset of the fecal community that was associated with carcinomas was as predictive as the full community.

>>>>

**Results.** We quantified the odds ratios for individual bacterial genera that were associated with an individual having tumors relative to a normal colon. Among the stool samples, there were no genera that had a significant odds ratio associated with adenoma and there were `r length(crc_OR_stool$measure)` genera with significant odds ratios (ORs) associated with carcinoma. Similarly, among the tissue samples, there were no genera that had a significant odds ratio associated with adenoma and there were `r length(crc_unmatched_OR_tissue$measure)` genera with significant odds ratios associated with carcinoma. Among the significant odds ratios, the association between individual taxa and tumor diagnosis was equal or below `r ifelse(max(crc_OR_stool$rr) > max(crc_unmatched_OR_tissue$rr), round(max(crc_OR_stool$rr), digits = 2), round(max(crc_unmatched_OR_tissue$rr), digits = 2))`. Because individual taxa had limited association with tumor diagnosis, we trained Random Forest classification models using only the taxa that had significant ORs, using the entire collection of taxa found in each study, and using operational taxonomic units defined based on a 97% similarity threshold. All training approaches yielded similar classification success as measured using the Area Under the Curve. The ability to correctly classify individuals with adenomas was poor and the ability to classify individuals with carcinomas was considerably better using sequences from stool or tissue.

**Importance.** This meta-analysis confirms previous results indicating that individuals with adenomas cannot be readily classified based on their bacterial community, but that those with carcinomas can. Regardless of the dataset, we found a subset of the fecal community that was associated with carcinomas was as predictive as the full community.

### 2018-03-03 submission/manuscript.tex
add importance, rm conclusion, change to sig OR only model

\textbf{Results.} We quantified the odds ratios for individual bacterial
genera that were associated with an individual having tumors relative to
a normal colon. Among the stool samples, there were no genera that had a
significant odds ratio associated with adenoma and there were 8 genera
with significant odds ratios associated with carcinoma. Similarly, among
the tissue samples, there were no genera that had a significant odds
ratio associated with adenoma and there were 3 genera with significant
odds ratios associated with carcinoma. Among the significant odds
ratios, the association between individual taxa and tumor diagnosis was
equal or below 7.11. Because individual taxa had limited association
with tumor diagnosis, we trained Random Forest classification models
using the genera with the five highest and lowest odds ratios, using the
entire collection of genera found in each study, and using operational
taxonomic units defined based on a 97\% similarity threshold. All
training approaches yielded similar classification success as measured
using the Area Under the Curve. The ability to correctly classify
individuals with adenomas was poor and the ability to classify
individuals with carcinomas was considerably better using sequences from
stool or tissue.

\textbf{Conclusions.} This meta-analysis confirms previous results
indicating that individuals with adenomas cannot be readily classified
based on their bacterial community, but that those with carcinomas can.
Regardless of the dataset, we found a subset of the fecal community that
was associated with carcinomas was as predictive as the full community.

>>>>

\textbf{Results.} We quantified the odds ratios for individual bacterial
genera that were associated with an individual having tumors relative to
a normal colon. Among the stool samples, there were no genera that had a
significant odds ratio associated with adenoma and there were 8 genera
with significant odds ratios (ORs) associated with carcinoma. Similarly,
among the tissue samples, there were no genera that had a significant
odds ratio associated with adenoma and there were 3 genera with
significant odds ratios associated with carcinoma. Among the significant
odds ratios, the association between individual taxa and tumor diagnosis
was equal or below 7.11. Because individual taxa had limited association
with tumor diagnosis, we trained Random Forest classification models
using only the taxa that had significant ORs, using the entire
collection of taxa found in each study, and using operational taxonomic
units defined based on a 97\% similarity threshold. All training
approaches yielded similar classification success as measured using the
Area Under the Curve. The ability to correctly classify individuals with
adenomas was poor and the ability to classify individuals with
carcinomas was considerably better using sequences from stool or tissue.

\textbf{Importance.} This meta-analysis confirms previous results
indicating that individuals with adenomas cannot be readily classified
based on their bacterial community, but that those with carcinomas can.
Regardless of the dataset, we found a subset of the fecal community that
was associated with carcinomas was as predictive as the full community.
